Wetting of the tarsal adhesive fluid controls underwater adhesion in ladybug beetles

### 2021-08-02 source/jeb_tex/manuscript.tex
sensitivity analysis and LMM analysis done
figures updated

\begin{figure*}
\centering
\includegraphics[width=6in]{Figure6-Model_effect_of_hair_size}
\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
hair tip diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
forces are calculated from the minima of the respective force-distance
curves, based on the capillary bridge model. A negative value represents
attraction. The air bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Pad diameter and bubble
volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
\end{figure*}
The tarsal hairs on a ladybug's adhesive pad terminate in various shapes, such as ``discoidal''
or ``pointed''. We studied this geometric effect on adhesion by
changing the hair tip diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
Here, the pad diameter, total hair contact area and bubble volume
are constant since $D_{p}$, $\alpha$ and $\hat{V}_{b}$ are kept
fixed. The tarsal adhesive fluid volume is again assumed to scale relative
to the hair diameter ($\phi_{f}=2$).

>>>>

\begin{figure}
%\centering
\includegraphics[width=3.5in]{Figure6-Model_effect_of_hair_size}
\caption{\label{fig:Effect-of-hair}Normalised adhesion force of a hairy pad on a hydrophilic and hydrophobic substrate as a function of
hair tip diameter, $D_{h}$. Volume of each fluid bridge, $V_{f}$, scales
relative to $D_{h}$ based on the parameter $\phi_{f}=2$. Adhesion
forces are calculated from the minima of the respective force-distance
curves, based on the capillary bridge model. A negative value represents
attraction. The air bubble's contribution to the net force for an \emph{underwater:
bubble} contact is denoted by plus symbols. Pad diameter and bubble
volume are kept fixed. All lengths are scaled relative to $D_{p}$.}
\end{figure}

The tarsal hairs on a ladybug's adhesive pad terminate in various shapes, such as ``discoidal''
or ``pointed''. We studied this geometric effect on adhesion by
changing the hair tip diameter, $D_{h}$ (Figure \ref{fig:Effect-of-hair}).
Here, the pad diameter, total hair contact area and bubble volume
are constant since $D_{p}$, $\alpha$ and $\hat{V}_{b}$ are kept
fixed. The tarsal adhesive fluid volume is again assumed to scale relative
to the hair diameter ($\phi_{f}=2$).
